### 2020-09-09 doc/manuscript/Dow_manuscript.Rmd
MVP of Fig1

Here, I’ll insert a reference to Sean’s paper (McMahon & Parker, 2015). This is pulled from references.bib.

@@

>>>>

Here, I’ll insert a reference to Sean’s paper [@mcmahon_general_2015]. This is pulled from references.bib.

@@

### Figures

```{r logistic-growth-model, out.width="100%", echo=FALSE, fig.align="center", fig.cap="Lorem ipsum"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig1.png")
```
